### 2024-02-06 chap_methodo/chap_methodo.tex
Appendices A, B and C post-reviews by FC

\subsection{Typical days to break the curse of dimensionality}
\label{subsec:meth:TD}
\textbf{Add here some details about TDs}

@@

\noindent
Compared to the perfect foresight, the myopic approach (Figure \ref{fig:my_schematic}) has two main advantages: shorter computational time and more realistic representation of the short-sightedness of decision-makers. For this reason, several studies are based on this approach \citep{babrowski2014reducing,poncelet2016myopic,nerini2017myopic,heuberger2018impact}. \citet{babrowski2014reducing} analysed the benefit of the myopic approach to reduce the computational time. \citet{poncelet2016myopic} uses this approach to analyse the expansion planning of the power sector beyond 2050. \citet{nerini2017myopic} analysed the impact of the horizon windows and overlapping time.  Overall these studies decided to choose the myopic approach to analyse the speed of change compared to a perfect foresight approach.
 % rajout du Réalisme 
Moreover, the myopic approach allows a sequential optimisation process that opens the doors to decision-making/policy-learning methodologies, like assessing shock events. This approach is used by \citet{heuberger2018impact} who assessed the speed of integration of technologies due to these events. 
In their analysis of the overcapacity in European power systems, \citet{moret2020overcapacity} emphasised that such a ``possibility of \textit{recourse}" is very appropriate to address uncertainty gradually unfolding over time. Consequently, the development of the myopic approach represents the foundations of the further implementation of the agent-based reinforcement learning framework (see Section \ref{sec:meth:RL}).\\

@@

\noindent
Besides being an in-house used method, an early step of this thesis consisted in assessing \gls{PCE} with similar approach used in the literature \cite{limpens2020impact}. \\

@@

to rank parameters among each other. In (\ref{eq:mu*}), $SF_{i}$ is the distribution formed by the $r$ standardized elementary effects, as done in \citet{Moret2017PhDThesis}.\\

>>>>

@@

\noindent
Compared to the perfect foresight, the myopic approach (Figure \ref{fig:my_schematic}) has two main advantages: shorter computational time and more realistic representation of the short-sightedness of decision-makers. For this reason, several studies are based on this approach \citep{babrowski2014reducing,poncelet2016myopic,nerini2017myopic,heuberger2018impact}. \citet{babrowski2014reducing} analysed the benefit of the myopic approach to reduce the computational time. \citet{poncelet2016myopic} uses this approach to analyse the expansion planning of the power sector beyond 2050. \citet{nerini2017myopic} analysed the impact of the horizon windows and overlapping time.  Overall these studies decided to choose the myopic approach to analyse the speed of change compared to a perfect foresight approach.
 % rajout du Réalisme 
Moreover, the myopic approach allows a sequential optimisation process that opens the doors to decision-making/policy-learning methodologies, like assessing shock events. This approach is used by \citet{heuberger2018impact} who assessed the speed of integration of technologies due to these events. 
In their analysis of the overcapacity in European power systems, \citet{moret2020overcapacity} emphasised that such a ``possibility of \textit{recourse}" is very appropriate to address uncertainty gradually unfolding over time. Consequently, the development of the myopic approach represents the foundations of the further implementation of the agent-based reinforcement learning framework (see Section \ref{sec:meth:RL}).

@@

\noindent
Besides being an in-house used method, an early step of this thesis consisted in assessing \gls{PCE} with similar approach used in the literature \cite{limpens2020impact}.

@@

to rank parameters among each other. In (\ref{eq:mu*}), $SF_{i}$ is the distribution formed by the $r$ standardized elementary effects, as done in \citet{Moret2017PhDThesis}.
